Monte Carlo tree search compared to A\(^*\) in airspace configuration decision problem

### 2018-05-22 article/article.tex

Accuracy can be quantitatively assessed by comparing the outcome of the MCTS
algorithm against the A\(^*\) cost and a greedy algorithm cost.
The time allowed to the MCTS to run is considered long enough to allow the MCTS
to converge to its best solution. The results are summarised in
table~\ref{tab:methods_compare}.
\begin{table}
  \centering
  \begin{tabulary}
    {\textwidth}{LRR}
    Alg.    & Cost  & Err.   \\
    \toprule
    A\(^*\) & 77.31 & 0\%    \\
    MCTS    & 82.48 & 6.7\%  \\
    Greedy  & 90.50 & 17.1\% \\
  \end{tabulary}
  \caption{Comparison of several methods on the generated
  scenario.}\label{tab:methods_compare}
\end{table}

The graph~\ref{fig:cmpdepth} shows the evolution of the difference of costs with
varying depth. The error rate is expected to grow as the depth increase since
the MCTS might fail to explore the best nodes among the exponentially growing
amount of them. The figure~\ref{fig:cmpdepth} does not show a constant growth of
error rate between MCTS and A\(^*\). As hoped, the MCTS remains always better
than the greedy algorithm.
\begin{figure}
  \begin{tikzpicture}
    \begin{axis}
      [line width=0.05, mark size=0.1, xlabel=depth, ylabel=cost,
      legend entries = {A\(^*\), MCTS, Greedy}, legend pos=south east]
      \foreach \i in {0, 1, 2} {%
        \addplot+ table [
          x expr = {\lineno + 1}, y index = \i ] {./data/cmpdepth.data};
      }
    \end{axis}
  \end{tikzpicture}
  \caption{Cost difference for varying depth with 0.5 seconds allowed to
    MCTS.}\label{fig:cmpdepth}
\end{figure}

>>>>

Accuracy can be quantitatively assessed by comparing the outcome of the MCTS
algorithm against the A\(^*\) cost and a greedy algorithm cost.
The time allowed to the MCTS to run is considered long enough to allow the MCTS
to converge to its best solution. The results are summarised in
table~\ref{tab:methods_compare}.
\begin{table}
  \centering
  \begin{tabulary}
    {\textwidth}{LRR}
    Alg.    & Cost  & Err.   \\
    \toprule
    A\(^*\) & 77.31 & 0\%    \\
    MCTS    & 82.48 & 6.7\%  \\
    Greedy  & 90.50 & 17.1\% \\
  \end{tabulary}
  \caption{Comparison of several methods on the generated
  scenario (\(\theta = 3\)).}\label{tab:methods_compare}
\end{table}

The graph~\ref{fig:cmpdepth} shows the evolution of the difference of costs with
varying depth. The error rate is expected to grow as the depth increase since
the MCTS might fail to explore the best nodes among the exponentially growing
amount of them. The figure~\ref{fig:cmpdepth} does not show a constant growth of
error rate between MCTS and A\(^*\). As hoped, the MCTS remains always better
than the greedy algorithm.
\begin{figure}
  \begin{tikzpicture}
    \begin{axis}
      [line width=0.05, mark size=0.1, xlabel=depth, ylabel=cost,
      legend entries = {A\(^*\), MCTS, Greedy}, legend pos=south east]
      \foreach \i in {0, 1, 2} {%
        \addplot+ table [
          x expr = {\lineno + 1}, y index = \i ] {./data/cmpdepth.data};
      }
    \end{axis}
  \end{tikzpicture}
  \caption{Cost difference for varying depth with 0.5 seconds allowed to
  MCTS and \(\theta = 3\).}\label{fig:cmpdepth}
\end{figure}
